---
title: "Question2"
author: "Soumyadip Mitra"
date: "8/1/2020"
output: html_document
---


## Is there any relationship between the amount of time spent working with individual clients (time to complete an assessment, time to complete resume, # of logged activities, etc.) and how quickly they are employed? 
– Contact+Hire+Act+Feedback+Q1+Q4+Q5–
(date calculation) – Mitra

This can be derived variable - 
Days_to_get_hired = Date_Turned_Blue__c - Date_turned_green__c

these are 2 intervals we need to use - 

Days_between_Assigned_and_Assessed = Dat_Initial_Assessment_was_Completed__c - Date_assigned_to_staff__c)

Days_between_Assessment_and_Resume = Date_Resume_Completed__c - Dat_Initial_Assessment_was_Completed__c

## Read the Data
```{r message=FALSE, warning=FALSE}
#library(readr)
df1 <- read.csv('Contact+Hire+Act+Feedback+Q1+Q4+Q5.csv')
```

## Format the date fields
```{r}
#df1$c_CreatedDate <- as.Date(df1$c_CreatedDate, format = "%m/%d/%y %I:%M:%S %p")
library(lubridate)
df1$c_Date_Turned_Blue__c <- date(mdy_hm(df1$c_Date_Turned_Blue__c))
df1$c_Date_turned_green__c <- date(mdy_hm(df1$c_Date_turned_green__c))
df1$c_Dat_Initial_Assessment_was_Completed__c <- date(mdy_hm(df1$c_Dat_Initial_Assessment_was_Completed__c))
df1$c_Date_assigned_to_staff__c <- date(mdy_hm(df1$c_Date_assigned_to_staff__c))
df1$c_Date_Resume_Completed__c <- date(mdy_hm(df1$c_Date_Resume_Completed__c))
```

## Select the formatted date columns in a subset and examine them
```{r}
myDF <- subset(df1, select = c(
  c_Date_Turned_Blue__c,
  c_Date_turned_green__c,
  c_Dat_Initial_Assessment_was_Completed__c,
  c_Date_assigned_to_staff__c,
  c_Date_Resume_Completed__c
  ))
# Empty the original dataset as its not required any more
df1 <- NULL
str(myDF)
```

## Examine the data sample
```{r}
head(myDF)
```


## Create 
- Days_to_get_hired = Date_Turned_Blue__c - Date_turned_green__c
- Days_between_Assigned_and_Assessed = c_Dat_Initial_Assessment_was_Completed__c - c_Date_assigned_to_staff__c
- Days_between_Assessment_and_Resume = c_Date_Resume_Completed__c - c_Dat_Initial_Assessment_was_Completed__c
- Time_spent_on_clients = Days_between_Assigned_and_Assessed + Days_between_Assessment_and_Resume
```{r}
library(dplyr)
myDF <- myDF %>% 
  mutate(Days_to_get_hired = c_Date_Turned_Blue__c - c_Date_turned_green__c) %>%
  mutate(Days_between_Assigned_and_Assessed = 
           c_Dat_Initial_Assessment_was_Completed__c - c_Date_assigned_to_staff__c) %>%
  mutate(Days_between_Assessment_and_Resume = 
           c_Date_Resume_Completed__c - c_Dat_Initial_Assessment_was_Completed__c) %>%
  mutate (Time_spent_on_clients = Days_between_Assigned_and_Assessed + Days_between_Assessment_and_Resume)
head(myDF)
```


## Keep the fields required
```{r}
finalDf <- subset(myDF, select = c(
  Days_to_get_hired,
  #Days_between_Assigned_and_Assessed,
  #Days_between_Assessment_and_Resume,
  Time_spent_on_clients
  ))
head(finalDf)
```


## Check the range of the two variables
```{r}
finalDf$Days_to_get_hired <- as.integer(finalDf$Days_to_get_hired)
finalDf$Time_spent_on_clients <- as.integer(finalDf$Time_spent_on_clients)
summary(finalDf)
#starwars %>% filter(mass > mean(mass, na.rm = TRUE))
```


## Remove rows with negative, zero and missing values
```{r}
finalDf <- finalDf %>% 
  filter(Days_to_get_hired > 0) %>%
  filter(Time_spent_on_clients > 0)
summary(finalDf)

```


## Boxplot before removing outliers
```{r}
library(ggplot2)
library(plotly)
bp <- finalDf %>% 
  ggplot(aes(x=1,y=Days_to_get_hired)) +
  geom_boxplot() +
  theme_minimal()
ggplotly(bp)
```


## Remove outliers
```{r}
finalDf <- finalDf %>% 
  filter(Days_to_get_hired < (1.5*(218-63))) %>%
  filter(Time_spent_on_clients < (1.5*(10-2)))
summary(finalDf)
```

## Boxplot after removing outliers
```{r}
bp <- finalDf %>% 
  ggplot(aes(x=1,y=Days_to_get_hired)) +
  geom_boxplot() +
  theme_minimal()
ggplotly(bp)
```


## Histogram of Days_to_get_hired
```{r}
ht <- finalDf %>%
  ggplot(aes(x=Days_to_get_hired)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white") +
  geom_density(fill="blue",alpha=0.3) + 
  theme_minimal()
ggplotly(ht)
```

## Plot the Time Spent on Clients vs Time to get hired with a Linear Regression Line
```{r}
p <- finalDf %>%
  ggplot(aes(x=Time_spent_on_clients,y=Days_to_get_hired)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  theme_minimal()
p
```



## Linear Model Statistics
```{r}
model <- lm(Days_to_get_hired ~ Time_spent_on_clients, data=finalDf)
summary(model)
```


